### 2019-12-03 Mathematical Statistics/04_sampling_distributions.rmd
mathematical statistics, ch 4 work
mathematical statistics, ch 4 work

>>>>

### 4.28

Let $X_1, X_2, \ldots, X_N \sim^{i.i.d.}$ with corresponding pdf $f(x) = 3x^2, 0 \le x \le 1$.

a.) Find the pdf for $X_{min}$.

b.) Find the pdf for $X_{max}$.

c.) If $n = 10$, find the probability that the largest value, $X_{max}$, is greater than 0.92.

### 4.29

Compute the pdf of the sampling distribution of the maximum samples of size 10 from a population with an exponential distribtuion with $\lambda = 12$.

### 4.30

Let $X_1, X_2, \ldots, X_N \sim^{i.i.d.} Exp(\lambda)$ with pdf $f(x) = \lambda e^{-\lambda x}, \lambda > 0, x > 0$.

a.) Find the pdf $f_{min}(x)$ for the sample minimum $X_{min}$. Recognize this as the pdf of a known distribution.

b.) Simulate in R the sampling distribution of $X_{min}$ of samples of size $n = 25$ from the exponential distribution with $\lambda = 7$.

Compare the theoretical expected value of $X_{min}$ with the simulated expected value.

### 4.31

Let $X_1, X_2, \ldots, X_n \sim^{i.i.d.} Pois(3)$. Let $X = \sum^{10}_{i=1}X_i$.

Find the pdf for the sampling distribution of X.

### 4.32

Let $X_1$ and $X_2$ be independent exponential random variables, both with parameter $\lambda > 0$.

Find the cumulative distribution function for the sampling distribution of $X = X_1 + X_2$.

### 4.33

This simulation illustrates the CLT for a finite population.

```{r, echo = T, fig.height=3.5, fig.width=8}
N <- 400
n <- 5

finpop <- rexp(N, 1/10)

ggplot(data.table(x = finpop)) +
   geom_histogram(aes(x, fill = ..count..)) +
   labs(title = "Exp(1/10)")

mean(finpop) #mean (mu) of your pop.
sd(finpop) # stdev (sigma) of your pop.
sd(finpop)/sqrt(n) # theoretical standard error of sampling distribution

sd(finpop)/sqrt(n) * sqrt((N-n)/(N-1)) # without replacement

Xbar <- numeric(1000)
for(i in 1:1000)
{
   x <- sample(finpop, n) # Random sample of size n
                          # (w/o replacement)
   Xbar[i] <- mean(x)
}

p1 <- ggplot(data.table(x = Xbar)) +
   geom_histogram(aes(x, fill = ..count..), bins = 30) +
   labs(title = "Mean Sampling Distribution Histogram")

p2 <- ggplot(data.table(x = Xbar), aes(sample = x)) +
   stat_qq() +
   stat_qq_line() +
   labs(title = "Mean Sampling Distribution QQ-Plot")

grid.arrange(p1, p2, nrow = 2)

mean(Xbar)
sd(Xbar) # estimated standard error of sampling distribution

a.) Does the sampling distribution of sample means appear approximately normal?

b.) Compare the mean and standard error of your simulated sampling distribution with the theoretical ones.

c.) Calculate $(\sigma/\sqrt(n))(\sqrt{(N-n)/(N-1)}$, where $\sigma$ is the standard deviation of the finite population and compare with the (estimated) standard error of the sampling distribution.

d.) Repeat for larger __n__, say __n__ = 20 and __n__ = 100.

### 4.34

Let $X_1, X_2, \ldots, X_n$ be independent random variables from $N(\mu, \sigma)$.

We are interested in the sampling distribution of the variance.

Run a simulation to draw random samples of size 20 from $N(25, 7^2)$ and calculate the variance for each sample.

```{r, echo = T, fig.height=3.5, fig.width=8}
W <- numeric(1000)

for(i in 1:1000)
{
   x <- rnorm(20, 25, 7)
   W[i] <- var(x)
}

mean(W)
var(W)

p1 <- ggplot(data.table(x = W)) +
   geom_histogram(aes(x, fill = ..count..), bins = 30) +
   labs(title = "Variance Sampling Distribution")

p2 <-
   ggplot(data.table(value = W), aes(sample = value)) +
   stat_qq() +
   stat_qq_line() +
   labs(title = "Mean Sampling Distribution QQ-Plot")

grid.arrange(p1, p2, nrow = 2)

Does the sampling distribution appear to be normally distributed?

Repeat with n = 50 and n = 200.

### 4.35

A random sample of size $n = 100$ is drawn from a distribution with pdf $f(x) = 3(1- x)^2, 0 \le x \le 1$.

a.) Use the CLT approximation to estimate $P(\bar{X} \le 0.27)$.

b.) Use the expanded CLT to estimate the same probability (dnorm).

c.) If $X_1, X_2, X_3 \sim^{i.i.d.} Unif[0, 1]$, then the minimum has density __f__ given above.

Use simulation to estimate the probability.
